### 2022-09-08 article/article.tex
prepare manuscript submission

@@

% Margins
\usepackage[margin=2cm]{geometry}

% Packages I've been using for differen reasons
\usepackage{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

@@

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil}

@@

We invited respondents from all regions of Brazil to participate in our
experiment. Qualtrics recruited 2,406 adult Brazilian citizens between October
30 and December 22, 2020 to take part in our survey experiment.\footnote{Our
ethics statement is available in Section E of the Supplementary Material.} We
included ten questions on demographics and other information that might
influence the results. These include the respondent's age, gender, ethnicity,
level of education, monthly family income, political orientation (left to
right), support for the death penalty, whether they had been victimized in the
last year, their trust in the police, and their trust in the judicial system.
We used these measures to disentangle heterogeneous effects in the main
responses. Descriptive statistics are available in Section B of the
Supplementary Material.

@@

\begin{figure}[ht]
\includegraphics[width=17cm]{conjoint-color.pdf}
\caption{Relative preferences for lynching-episode attributes (marginal means)}
\centering
\label{fig:exp01}
\end{figure}

@@

\begin{table}[ht] \centering
  \caption{Average treatment effects for experiment 3}
  \label{tab:exp03main}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
\hline \\[-1.8ex]
 Constitution and penal code & -4.509^{**} &  &  &  \\
  & (1.805) &  &  &  \\
  Human rights &  & -1.571 &  &  \\
  &  & (1.801) &  &  \\
  Vendettas &  &  & -3.156^{*} &  \\
  &  &  & (1.879) &  \\
  Combined treatments &  &  &  & -3.023^{**} \\
  &  &  &  & (1.493) \\
  Constant & 40.823^{***} & 40.823^{***} & 40.823^{***} & 40.823^{***} \\
  & (1.293) & (1.293) & (1.293) & (1.293) \\
 N & \multicolumn{1}{c}{1,114} & \multicolumn{1}{c}{1,173} & \multicolumn{1}{c}{1,092} & \multicolumn{1}{c}{2,215} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
\end{tabular}
\end{table}
\normalsize

@@

Our last treatment, which raises the possibility of sparking vendettas, has a
large, negative effect on support for lynchings. Mentioning that lynchings
trigger cycles of violence has a negative effect of about 8 percent when
compared with the control group. While we expected that the coefficient for
this treatment condition would be larger than that for the treatment on legal
punishments, the means of both groups are not statistically different from each
other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). As with the
other experiments, the results remain stable when we conduct subgroup analyses.

@@

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

% Bibliography
\bibliography{references.bib}

>>>>

% Endnotes
\usepackage{endnotes}
\let\footnote\endnote
\def\footnotetext{\endnotetext[\number\numexpr\value{endnote}+1]}
\let\footnotemark\endnotemark

@@

% Margins
\usepackage[margin=3cm]{geometry}

% Packages I've been using for different reasons
\usepackage{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

@@

% Title
\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil}

@@

We recruited 2,406 adult Brazilian citizens between October 30 and December 22,
2020 to participate in our survey experiment.\footnote{Our ethics statement is
available in Section E of the Supplementary Material.} We included ten
questions on demographics and other information that might influence the
results. These include the respondent's age, gender, ethnicity, level of
education, monthly family income, political orientation (left to right),
support for the death penalty, whether they had been victimized in the last
year, their trust in the police, and their trust in the judicial system. We
used these measures to disentangle heterogeneous effects in the main responses.
Descriptive statistics are available in Section B of the Supplementary
Material.

@@

\begin{figure}[ht]
\includegraphics[width=15cm]{conjoint-color.pdf}
\caption{Relative preferences for lynching-episode attributes (marginal means)}
\centering
\label{fig:exp01}
\end{figure}

@@

\begin{table}[ht] \centering
  \caption{Average treatment effects for experiment 3}
  \label{tab:exp03main}
  \addtolength{\tabcolsep}{-0.3em}
\begin{tabular}{@{\extracolsep{.01pt}}lD{.}{.}{-5} D{.}{.}{-5} D{.}{.}{-5} D{.}{.}{-5} }
\\[-2.5ex]\hline \\[-2ex]
\\[-2.5ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-2.5ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
\hline \\[-2ex]
 Constitution and penal code & -4.509^{**} &  &  &  \\
  & (1.805) &  &  &  \\
  Human rights &  & -1.571 &  &  \\
  &  & (1.801) &  &  \\
  Vendettas &  &  & -3.156^{*} &  \\
  &  &  & (1.879) &  \\
  Combined treatments &  &  &  & -3.023^{**} \\
  &  &  &  & (1.493) \\
  Constant & 40.823^{***} & 40.823^{***} & 40.823^{***} & 40.823^{***} \\
  & (1.293) & (1.293) & (1.293) & (1.293) \\
 N & \multicolumn{1}{c}{1,114} & \multicolumn{1}{c}{1,173} & \multicolumn{1}{c}{1,092} & \multicolumn{1}{c}{2,215} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
\end{tabular}
\end{table}
\normalsize

@@

Our last treatment, which raises the possibility of sparking vendettas, has a
large, negative effect on support for lynchings. Mentioning that lynchings
trigger cycles of violence has a negative effect of about 8 percent when
compared with the control group. While we expected that the coefficient for
this treatment condition would be larger than that for the treatment on legal
punishments, the means of both groups are not statistically different from each
other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). The results
remain stable in the subgroup analyses.

@@

% Endnotes
\renewcommand {\footnotesize} {\normalsize}
\theendnotes

% Bibliography
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}
\bibliography{references.bib}

### 2022-09-08 cover-letter/cover-letter.Rmd
prepare manuscript submission

* Danilo Freire: Senior Lecturer, School of Social and Political Sciences,
  University of Lincoln, <dfreire@lincoln.ac.uk>,
  <https://danilofreire.github.io>. Corresponding author.

* David Skarbek, Associate Professor, Department of Political Science, Brown
  University, <david_skarbek@brown.edu>, <http://davidskarbek.com>.

>>>>

* Danilo Freire: Senior Lecturer, School of Social and Political Sciences,
  University of Lincoln, Brayford Pool, Lincoln, Lincolnshire LN6 7TS, United Kingdom, `+44 077-630-647-58`, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
  Corresponding author.

* David Skarbek, Associate Professor, Department of Political Science, Brown
  University, 111 Thayer Street, Third Floor, Providence, RI 02912, United States of America, `+1 401-863-2825`, <david_skarbek@brown.edu>, <http://davidskarbek.com>, <https://twitter.com/davidskarbek>.
